p-CAPTCHAs and the Recognition Problem

### 2012-02-17 frostedglass/paper.tex
Improved the graphics.

\documentclass[12pt]{article}
\usepackage{graphicx}
%\usepackage{subfig}
%\usepackage{float}
%\floatstyle{boxed}
%\restylefigure{float}

@@

% Resistance to brute force key searching by use of CAPTCHAs:
% The idea—encrypt a CAPTCHA--2 pages (make this very clear, remember that it took awhile for Rob to grasp)
% Cite the other guys' paper early on. State that this is a different implementation of the idea.
% Value added: a different CAPTCHA, easier to implement. (Much more extensive discussion of the recognition problem)
% applications—resistance to a really fast computer, passwords-1 page
% ways that a person might attack the CAPTCHA—2 pages
	% scoring function
	% letter position minimization problem
	% puzzle pieces attack
	% human identifies parts of letters
% fortifications against an attack—2 pages
	% tweaking the parameters (window of readability)
	% letter offsetting
	% adding spurious connections/fake letters
% results of people trying to break it
% 
% A p-CAPTCHA system must have a CAPTCHA (so the computer cannot read the original), and a recognition problem.
% You must not allow the user to meaningfully recognize pieces of the original (because she could tell the computer what the pieces are and then the computer could solve a math problem)

@@

	Laptyeva et al. \cite{laptyeva} present a technique to resist a brute-force attack even when the decryption key space is small. Their approach is to focus on strengthening the difficulty of the recognition problem through the use of a Completely Automated Public Turing test to tell Computers and Humans Apart (CAPTCHA). In Laptyeva et al's system, the encryption key (EK) (which is also used as the decryption key) is the sum of a short password (SP) that the user memorizes, and a strong key (SK) that the computer provides. $EK = SP + SK$. SK is text in the form of a hard to recognize CAPTCHA-ized image, which they call a p-CAPTCHA. The image of SK is not stored on the computer, but rather a transformed version of it. In order to obtain the image of SK, the user types in SP which the computer uses to run the transformation process in reverse to obtain the image of SK. At this point, the computer shows the image of SK to a human who then types it in.

@@

    This introduces a metric on how quickly a true image can be found. Suppose that we have $n_{SP}$ potential decryption keys with one being the true decryption key: 
$SP_1, SP_2, \ldots, SP_{k-1}, SP_{true}, SP_{k+1}, \ldots SP_n$.
Associated with each decryption key is a candidate image, $IM_k$, which is a reverse transformation of the transformed image of the strong key, SK:
$$IM_1, IM_2, \ldots, IM_{k-1}, IM_{true}, IM_{k+1}, \ldots, IM_n.$$
Let $R$ be a recognition oracle that attempts to find the true plaintext by solving an optimization problem. Because of the large number of possible plaintexts, and the fact that an attacker does not know what the plaintext is, we will model the score from the recognition oracle as a random variable, with a distribution that depends on $R$. Because $IM_{true}$ may look a little different from other candidate images, we will say that
%$$R\left(IM_k\right) = \langleY ~ F(\textbf{\theta}), $$
 \begin{displaymath}
   R\left(IM_k\right) = \left\{
     \begin{array}{lr}
       X_k \sim f(x; \mathbf{\theta}) & \hbox{if } IM_k \neq IM_{true}\\
       Y \sim g(y; \mathbf{\lambda}) & \hbox{if } IM_k = IM_{true}
     \end{array}
   \right.
\end{displaymath}
where random variable $Y$ may be distributed differently than each $X_k$, but the $X_k$'s are treated as though they were independent and identically distributed.
%Stuff about order statistics?
Once the candidate plaintext images are ranked, the computer could show them to a human who could then recognize the true image. Because human labor is costly, this approach will have a feasibilty constraint, $n_f$. This approach will be feasible if the expected rank of the true image is less than $n_f$ (i.e. it is expected that no more than $n_f$ images will be ranked as more likely to be the true plaintext). If ranking an image is faster then trying to read a CAPTCHA, and the computer can eventually read the CAPTCHA, then $n_f$ could also represent the point at which the process takes too long for a computer.

@@

%Window of readibility--In order for a p-CAPTCHA system to be successful, the plaintext must be sufficiently a sufficiently strong CAPTCHA that a human can read it but a computer cannot. In the fuzzy letter tiles CAPTCHA,  The boundary between readable and unreadable plaintext may not be a

@@

\subsection*{Fuzzy Letter Tiles}
	Another p-CAPTCHA encryption method involves rearranging tiles of hard to recognize “fuzzy” letters. An example of this method is given in figure 1. First, a strong key (SK) is written as an image with warped and randomly offset letters. Second, random pixels are XORed between black and white to remove the presence of well-defined edges. Third, the image is partitioned into tiles. Fourth, the tiles are rearranged according to a permutation identified by the short password (SP).

\begin{figure}
	\includegraphics[scale=.5]{warpedSK.png}
	\includegraphics[scale=.5]{warpedfrosty.png}
	\includegraphics[scale=.5]{SKBreakLines.jpg}
	\includegraphics[scale=.5]{SK75391.png}
	\caption{The encryption process: 1. The strong key 2. Adding noise to hide edges 3. Dividing the image into tiles 4. Permuting the tiles according to a short password}
\label{EncryptionProcess}
\end{figure}

%\begin{figure}
%	\centering	
%	\subfloat{\label{fig:warpedSK}\includegraphics[width=.25]{warpedSK.png}}
%	\subfloat{\label{fig:warpedfrosty}\includegraphics[width=.25]{warpedfrosty.png}}
%	\subfloat{\label{fig:SKbreaklines}\includegraphics[width=.25]{SKbreaklines.png}}
%	\subfloat{\label{fig:SK75391}\includegraphics[width=.25]{SK75391.png}}
%	\caption{The encryption process: 1. The strong key 2. Adding noise to hide edges 3. Dividing the image into tiles 4. Permuting the tiles according to a short password}
%	\label{fig:EncryptionProcess}
%\end{figure}

@@

	The image above was encrypted by permuting 57 blocks. Although there are 57-factorial permutations of 57 blocks, most of these permutations are irrelevant. Each permutation must be tied to a decryption key in order for it to be found by the user. Since we are assuming that the decryption algorithm is known, an attacker will only have to deal with as many candidate images as the decryption algorithm will produce from the small decryption key space.

	Successfully attacking the p-CAPTCHA system presented here requires differentiating the true plaintext from the $n_{sp}$ candidate plaintexts. Three spurious plaintexts along with the true plaintext are shown in figure two.

\begin{figure}
	\includegraphics[scale=.5]{SK75392.png}
	\includegraphics[scale=.5]{SK75393.png}
	\includegraphics[scale=.5]{warpedfrosty.png}
	\includegraphics[scale=.5]{SK75395.png}
	\caption{Can your computer recognize the true plaintext?}
\label{RecognitionProblem}
\end{figure}

%\begin{figure}
%	\centering
%	\subfloat{\label{fig:SK75393}\includegraphics[width=.25]{SK75393.png}}
%	\subfloat{\label{fig:SK75392}\includegraphics[width=.25]{SK75392.png}}
%	\subfloat{\label{fig:warpedfrosty}\includegraphics[width=.25]{warpedfrosty.png}}
%	\subfloat{\label{fig:SK75394}\includegraphics[width=.25]{SK75394.png}}
%	\caption{Can your computer recognize the true plaintext?}
%	\label{fig:RecognitionProblem}
%\end{figure}

Some parameters of this system could be adjusted, such as the size of the letters, the amount of fuzziness (noise) in the background and in the letters, and the size of the tiles that get permuted. We do not want our tiles to be so small that permuting them makes the image look like pure noise, with no semblance of letters. We also do not want our tiles to be so large that a good portion of the letter is contained in each tile. While this would make the scrambled plaintext look a lot like the true plaintext, a human could figure out what letters were being used by looking at a scrambled image. By entering typing these letters into the computer, the computer could then try just brute force attacking with permutations of these letters without needing to solve any OCR problem.

%Advantage: easy to try different configurations of fonts, text size, fuzziness, tile sizes, etc.
%My system is easy to understand and implement.

%\section*{Stuff}
%(I want to include some these things in my paper, but I still don't know where I will fit them in.)

%The image orientation CORTCHA thing won't work.

@Article{,
author = {T. V. Laptyeva, S. Flach, K. Kladko},
title = {The Weak-password problem: Chaos, criticality, and encrypted p-CAPTCHAs},
journal = {EPL},
year = {2011},
OPTkey = {•},
OPTvolume = {95},
OPTnumber = {•},
OPTpages = {•},
OPTmonth = {•},
OPTnote = {•},
OPTannote = {•}
}
\begin{thebibliography}
\bibliography{laptyeva}
%\bibitem{laptyeva} \Author{She's Ukranian.}
\end{thebibliography}

>>>>

\documentclass[12pt]{article}
\usepackage{graphicx}

@@

@@

	Laptyeva et al. present a technique to resist a brute-force attack even when the decryption key space is small \cite{laptyeva}. Their approach is to focus on strengthening the difficulty of the recognition problem through the use of a Completely Automated Public Turing test to tell Computers and Humans Apart (CAPTCHA). In Laptyeva et al's system, the encryption key (EK) (which is also used as the decryption key) is the sum of a short password (SP) that the user memorizes, and a strong key (SK) that the computer provides. $EK = SP + SK$. SK is text in the form of a hard to recognize CAPTCHA-ized image, which they call a p-CAPTCHA. The image of SK is not stored on the computer, but rather a transformed version of it. In order to obtain the image of SK, the user types in SP which the computer uses to run the transformation process in reverse to obtain the image of SK. At this point, the computer shows the image of SK to a human who then types it in.

@@

    This introduces a metric on how quickly a true image can be found. Suppose that we have $n_{SP}$ potential decryption keys with one being the true decryption key: 
$SP_1, SP_2, \ldots, SP_{k-1}, SP_{true}, SP_{k+1}, \ldots SP_n$.
Associated with each decryption key is a candidate image, $IM_k$, which is a reverse transformation of the transformed image of the strong key, SK:
$$IM_1, IM_2, \ldots, IM_{k-1}, IM_{true}, IM_{k+1}, \ldots, IM_n.$$
Let $R$ be a recognition oracle that attempts to find the true plaintext by solving an optimization problem. Because of the large number of possible plaintexts, and the fact that an attacker does not know what the plaintext is, we will model the score from the recognition oracle as a random variable, with a distribution that depends on $R$. Because $IM_{true}$ may look a little different from other candidate images, we will say that
\begin{displaymath}
   R\left(IM_k\right) = \left\{
     \begin{array}{lr}
       X_k \sim f(x; \mathbf{\theta}) & \hbox{if } IM_k \neq IM_{true}\\
       Y \sim g(y; \mathbf{\lambda}) & \hbox{if } IM_k = IM_{true}
     \end{array}
   \right.
\end{displaymath}
where random variable $Y$ may be distributed differently than each $X_k$, but the $X_k$'s are treated as though they were independent and identically distributed.
%Stuff about order statistics?
Once the candidate plaintext images are ranked, the computer could show them to a human who could then recognize the true image. Because human labor is costly, this approach will have a feasibilty constraint, $n_f$. This approach will be feasible if the expected rank of the true image is less than $n_f$ (i.e. it is expected that no more than $n_f$ images will be ranked as more likely to be the true plaintext). If ranking an image is faster then trying to read a CAPTCHA, and the computer can eventually read the CAPTCHA, then $n_f$ could also represent the point at which the process takes too long for a computer.

@@

\begin{figure}
	\begin{center}
		\includegraphics[scale=.37]{CAPTCHA_Levels.png}
	\end{center}
	\caption{A p-CAPTCHA system not only requires that a computer cannot read a CAPTCHA, but that it cannot recognize it either. This narrows the range of possible images.}
\label{CAPTCHALevels}
\end{figure}

@@

\subsection*{Fuzzy Letter Tiles}
	Another p-CAPTCHA encryption method involves rearranging tiles of hard to recognize “fuzzy” letters. An example of this method is given in Figure~{\ref{EncryptionProcess}}. First, a strong key (SK) is written as an image with warped and randomly offset letters. Second, random pixels are XORed between black and white to remove the presence of well-defined edges. Third, the image is partitioned into tiles. Fourth, the tiles are rearranged according to a permutation identified by the short password (SP).

\begin{figure}
	\begin{center}
		\includegraphics[scale=.5]{EncryptionProcess.png}
	\end{center}
	\caption{The encryption process: 1. The strong key 2. Adding noise to hide edges 3. Dividing the image into tiles 4. Permuting the tiles according to a short password}
\label{EncryptionProcess}
\end{figure}

%\begin{figure}
%	\includegraphics[scale=.4]{warpedSK.png}
%	\includegraphics[scale=.4]{warpedfrosty.png}
%	\includegraphics[scale=.4]{SKBreakLines.jpg}
%	\includegraphics[scale=.4]{SK75391.png}
%	\caption{The encryption process: 1. The strong key 2. Adding noise to hide edges 3. Dividing the image into tiles 4. Permuting the tiles according to a short password}
%\label{EncryptionProcess}
%\end{figure}

@@

	The p-CAPTCHA plaintext in Figure~{\ref{EncryptionProcess}} encrypted by permuting 57 blocks. Although there are 57-factorial permutations of 57 blocks, most of these permutations are irrelevant. Each permutation must be tied to a decryption key in order for it to be found by the user. Since we are assuming that the decryption algorithm is known, an attacker will only have to deal with as many candidate images as the decryption algorithm will produce from the small decryption key space.

	Successfully attacking the p-CAPTCHA system presented here requires differentiating the true plaintext from the $n_{sp}$ candidate plaintexts. Three spurious plaintexts along with the true plaintext are shown in Figure~{\ref{RecognitionProblem}.

\begin{figure}
	\begin{center}
		\includegraphics[scale=.5]{RecognitionProblem.png}
	\end{center}
	\caption{Can your computer recognize the true plaintext?}
\label{RecognitionProblem}
\end{figure}

%\begin{figure}
%	\includegraphics[scale=.4]{SK75392.png}
%	\includegraphics[scale=.4]{SK75393.png}
%	\includegraphics[scale=.4]{warpedfrosty.png}
%	\includegraphics[scale=.4]{SK75395.png}
%	\caption{Can your computer recognize the true plaintext?}
%\label{RecognitionProblem}
%\end{figure}

Some parameters of this system could be adjusted, such as the size of the letters, the amount of fuzziness (noise) in the background and in the letters, and the size of the tiles that get permuted. By adjusting these parameters, we can better position ourselves in the window of possible images that are too difficult for a human to recognize, but still possible for a human to read without confusing the letters.

Some care should be taken when choosing parameters. We do not want our tiles to be so small that permuting them makes the image look like pure noise, with no semblance of letters. We also do not want our tiles to be so large that a good portion of the letter is contained in each tile. While this would make the scrambled plaintext look a lot like the true plaintext, a human could figure out what letters were being used by looking at a scrambled image. By typing these letters into the computer, the computer could then try a brute force attack with permutations of these letters without needing to solve any OCR problem.

\begin{thebibliography}
\bibliography{laptyeva}

	\bibitem{laptyeva}
		T. V. Laptyeva, S. Flach, K. Kladko

	%author = {T. V. Laptyeva, S. Flach, K. Kladko},
	%title = {The Weak-password problem: Chaos, criticality, and encrypted p-CAPTCHAs},
	%journal = {EPL},
	%year = {2011},
	%OPTvolume = {95}

%@Article{laptyeva,
%author = {T. V. Laptyeva, S. Flach, K. Kladko},
%title = {The Weak-password problem: Chaos, criticality, and encrypted p-CAPTCHAs},
%journal = {EPL},
%year = {2011},
%OPTvolume = {95}
}

%\bibitem{laptyeva} \Author{She's Ukranian.}
\end{thebibliography}
